A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Simplify descriptive statistics

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings
    n <- sapply(x, \(v) sum(!is.na(v)))
    labels <- paste0(names(x), " (N=", n, ")")
    idx <- which(sapply(x, is.numeric))
    names(x) <- names(x) |>
      replace(
        list = idx,
        values = labels[idx]
      )
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, output = "flextable", dinm = FALSE) |>
  flextable::theme_apa() |>
  flextable::font(fontname = "TeX Gyre Termes", part = "all")

@@

```{r}
#| label: "variables"
#| echo: false

>>>>

dat_desc <- dat

dat_desc$sex[is.na(dat_desc$sex)] <- "unknown" # Convert NA to "unknown"
dat_desc$year <- as.factor(dat_desc$year) # Convert year to factor

# Add number of non-missings to names of numeric variables
n <- sapply(dat_desc, \(v) sum(!is.na(v))) # Calculate number of non-missings
labels <- paste0(names(dat_desc), " (N=", n, ")") # Paste variable names and numbers together
idx <- which(sapply(dat_desc, is.numeric)) # Identify numeric variables
names(dat_desc)[idx] <- labels[idx] # Change the variable names

modelsummary::datasummary_balance(
  formula = ~ sex,
  data = dat_desc,
  output = "flextable",
  dinm = FALSE
) |>
  flextable::theme_apa() |>
  flextable::font(fontname = "TeX Gyre Termes", part = "all")

@@

```{r}
#| label: "bill-lengths"
#| echo: false
